---
title: "SM 727"
author: "Adam Kaderabek"
date: "9/30/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(faraway)
library(ggplot2)
library(tidyverse)
library(janitor)
library(haven)
```

# Please write down the R command(s) needed after each question! There is a total of 22 questions.

### Data types
# 1. Which command do you use to determine the type of an object?

The native R command is typeof(), with the object referenced in the parentheses.

# 2. What is the type of vector A?
```{r}
A <- c("2", "3", "4", "5", "6", "7", "8")
typeof(A) 
```
# 3. Convert A into an integer vector
```{r}
as.integer(A)
```
# 4. Create an integer vector B containing the numbers one through ten
```{r}
B <- c(1L:10L)
```
# 5. Create a new vector C from B which has the type "double"
```{r}
C <- as.double(B)
```
# 6. Change the third value of B to "3.5"
```{r}
B[B==3]<-3.5
```
# 7. Did this affect the type of B? How?
Yes. Type was converted to number.

### Reading in data
_Download both the Angell.dta (Stata data format) dataset and the Angell.txt dataset from this website https://stats.idre.ucla.edu/stata/examples/ara/applied-regression-analysis-by-fox-data-files/_

# 8. Read in the .dta version and store in an object called angell_stata
```{r}
AngeLL_strata <- read_dta("https://stats.idre.ucla.edu/stat/stata/examples/ara/angell.dta")
```
# 9. Read in the .txt version and store it in an object called angell_txt
```{r}
angell_txt <- read.table("https://stats.idre.ucla.edu/wp-content/uploads/2016/02/angell.txt")
```
# 10. Drop the first five observations in the angell_txt object
```{r}
angell_txt <- angell_txt[-c(1:5),]
```
# 11. Select columns 2 and 3 of the agell_stata object and store them in a new object called angell_small
```{r}
angell_small <- AngeLL_strata[c(1:43), c(2,3)]
```

# 12. Install the "MASS" package, load the package. Then, load the Boston dataset.
```{r}
install.packages('MASS')
data(Boston, package = "MASS")
```
# 13. What is the type of the Boston object?
```{r}
typeof(Boston)
```

#14. What is the class of the Boston object?
```{r}
class(Boston)
```
### Basic data summarizing and description
# 15. How many of the suburbs in the Boston data set bound the Charles river?
```{r}
table(Boston$chas, Boston$chas == 1)
```
# 16. Do any of the suburbs of Boston appear to have particularly high crime rates? Tax rates? Pupil-teacher ratios? Comment on the range of each variable.

```{r}
# crim - per capita crime rate by town.
summary(Boston$crim)
hist(Boston$crim,na.rm=T)
plot(Boston$crim)
abline(mean(Boston$crim,na.rm=T),0,col="red",lwd=2)
boxplot(Boston$crim,na.rm=T)
``` 


```{r}
#tax - full value property tax rate per $10,000.
summary(Boston$tax)
hist(Boston$tax,na.rm=T)
plot(Boston$tax)
abline(mean(Boston$tax,na.rm=T),0,col="red",lwd=2)
boxplot(Boston$tax,na.rm=T)
```


```{r}
# ptratio - pupil:teacher ratio by town.
summary(Boston$ptratio)
hist(Boston$ptratio,na.rm=T)
plot(Boston$ptratio)
abline(mean(Boston$ptratio,na.rm=T),0,col="red",lwd=2)
boxplot(Boston$ptratio,na.rm=T)
```


# 17. What is the median pupil-teacher ratio among the towns in this data set that have a per capita crime rate larger than 1?
```{r}
subpt <- subset(Boston, Boston$crim >= 1)
summary(subpt$ptratio)
```

### Functions
# 18. Write a function that calculates the squareroot of an integer
```{r}
fix_missing <- function(x) {
  x[x == -99] <- NA # read: replace the subset of values in x where x equals -99 with NA!
  x
}
sri <- function(x) {
  y <- ifelse(is.integer(x), sqrt(x), "Value X is not an integer")
  y
}
sri(4)
```
# 19. Write a function that calculates 95% confidence intervals for a point estimate. The function should be called "my.CI". When called with "my.CI(2, 0.2)", the output of the function should read "The 95% CI upper bound of point estimate 2 with standard error 0.2 is 2.392. The lower bound is 1.608." _Note: the function should take a point estimate and its standard error as arguments. You may use the formula for 95% CI: point estimate +/- 1.96*standard error._

# 20. Write a function that converts all negative numbers in the following dataset into NA. Use as little code as possible and try to avoid code repetition.
```{r}
set.seed(1002)
df <- data.frame(replicate(10, sample(c(1:10, c(-99,-98,-5)), 6, rep = TRUE)))
names(df) <- letters[1:6]
df

NegNA <- function(x) {
  x[x < 0] <- NA #replace the subset of values in x where x is a negative number (i.e. less than 0) with NA
  x
}
```
# 21. Use your function to convert all negative numbers in the dataset into NA without changing the class of the object
```{r}
NegNA(df)
class(df) #object class is still data.frame
```
# 22. Change the function you wrote above such that it turns any negative number into NA!
My function does turn any negative number of an object to NA. 